Approximation as Differentiation

### 2025-07-10 main/definability.tex
laird07, fix ref.
Citations.

\begin{remark}
  We have formalised \thmref{glr-definability} and
  \thmref{language-definability} in Agda, except for the fact that
  $\Fam(C)$ is extensive\footnote{For reviewers: we intend to fix this
    before any final version.}. Our formalisation uses E-categories
  (\cite{palmgren-wilander}) so we cannot state
  \thmref{glr-definability} as given because the concept of strict
  preservation does not make sense. Therefore, the formalised version
  of \thmref{thm:language-definability} is ``up to isomorphism''.

  We believe that this result also extends to the list type, since it
  is constructed from an infinte coproduct, but have not yet checked
  all the details.
\end{remark}

>>>>

\begin{remark}
  We have formalised \thmref{glr-definability} and
  \thmref{language-definability} in Agda, except for the fact that
  $\Fam(C)$ is extensive\footnote{For reviewers: we intend to fix this
    before any final version.}. Our formalisation uses E-categories
  (\cite{palmgren-wilander}) so we cannot state
  \thmref{glr-definability} as given because the concept of strict
  preservation does not make sense. Therefore, the formalised version
  of \thmref{language-definability} is ``up to isomorphism''.

  We believe that this result also extends to the list type, since it
  is constructed from an infinite coproduct, but have not yet checked
  all the details.
\end{remark}

### 2025-07-10 main/models.tex
Citations.

\begin{definition}
  \item
  \begin{enumerate}
  \item The category $\LatGal$ has bounded lattices as objects and
    Galois connections as morphisms, with the right adjunct going in
    the ``forward'' direction.
  \item The category $\MeetSLat$ has meet-semilattices with top as
    objects and monotone finite meet preserving functions as
    morphisms.
  \item The category $\JoinSLat$ has join-semilattices with bottom as
    objects and monotone finite join preserving functions as
    morphisms.
  \end{enumerate}
\end{definition}

>>>>

\begin{definition}
  \item
  \begin{enumerate}
  \item The category $\LatGal$ has bounded lattices as objects and
    Galois connections as morphisms, with the right adjunct going in
    the ``forward'' direction.
  \item The category $\MeetSLat$ has meet-semilattices with top as
    objects and finite meet preserving functions as
    morphisms.
  \item The category $\JoinSLat$ has join-semilattices with bottom as
    objects and finite join preserving functions as
    morphisms.
  \end{enumerate}
\end{definition}
